|

### 2021-03-16 appendix/appendix.Rmd
build estimator for heterogeneous effects ma

# Broom the multi-level model
broom_mod <- function(mod) {
  aux <- data.frame(predict(mod))
  mod2 <- tibble(
    TE = as.numeric(mod$yi),
    seTE = sqrt(mod$vi),
    studlab = mod$slab,
    lower = as.numeric(mod$yi)-1.96*sqrt(mod$vi),
    upper = as.numeric(mod$yi)+1.96*sqrt(mod$vi),
    group = 'A') %>%
    bind_rows(.,
              aux = tibble(
                TE = c(aux$pred, NA),
                seTE = c(aux$se, NA),
                studlab = c("Overall Effect",
                            "Prediction Interval"),
                lower = c(aux$ci.lb,
                          aux$cr.lb),
                upper = c(aux$ci.ub,
                          aux$cr.ub),
                group = "B")) %>%
    group_by(studlab) %>%
    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
    ungroup()
  return(mod2)
}

@@

# Build forest plot for heterogeneous analysis
# Build plot function for forest plots
build_forest_het <- function(mod, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
  mod <- update(mod, byvar = hetvar, print.byvar = F)

>>>>

# Broom the multi-level model
broom_mod <- function(mod, subgroup = FALSE) {
  aux <- data.frame(predict(mod))
  if (subgroup) {
    teeff = aux$pred
    seteeff = aux$se
    labeff = c("Subgroup Effect")
    loeff = c(aux$ci.lb)
    upeff = c(aux$ci.ub)
  } else {
    teeff = c(aux$pred, NA)
    seteeff = c(aux$se, NA)
    labeff = c("Overall Effect",
               "Prediction Interval")
    loeff = c(aux$ci.lb, aux$cr.lb)
    upeff = c(aux$ci.ub, aux$cr.ub)
  }
  mod2 <- tibble(
    TE = as.numeric(mod$yi),
    seTE = sqrt(mod$vi),
    studlab = mod$slab,
    lower = as.numeric(mod$yi)-1.96*sqrt(mod$vi),
    upper = as.numeric(mod$yi)+1.96*sqrt(mod$vi),
    group = 'A') %>%
    bind_rows(.,
              aux = tibble(
                TE = teeff,
                seTE = seteeff,
                studlab = labeff,
                lower = loeff,
                upper = upeff,
                group = "B")) %>%
    group_by(studlab) %>%
    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
    ungroup()
  return(mod2)
}

# Estimation of the 
estim_het <- function(dat, yi, v, random, slab, hetvar = NULL) {
  if (is.null(hetvar)) {
    print('Hetvar should be different than null.')
    break
  }
  levshetvar <- unique(hetvar)
  fullmod <- rma.mv(yi = yi, V = v, random = random,
                    data = dat, slab = slab, method = 'REML',
                    test = 't', tdist = T)
  res <- tibble()
  for (i in levshetvar) {
    partmod <- rma.mv(yi = yi, V = v, 
                      random = random,
                      data = dat, slab = slab, 
                      method = 'REML',
                      test = 't', tdist = T, 
                      subset = hetvar == i)
    partmod <- broom_mod(partmod, subgroup = T)
    partmod$byvar = i
    partmod <- bind_rows(
      tibble(TE = NA, seTE = NA,
             studlab = toupper(i), lower = NA,
             upper = NA, group = "B", byvar = i),
      partmod
    )
    res <- bind_rows(res, partmod)
  }
  aux <- data.frame(predict(fullmod))
  res <- bind_rows(res,
                   tibble(
                     byvar = NA,
                     TE = c(aux$pred, NA),
                     seTE = c(aux$se, NA),
                     studlab = c("Overall Effect", "Prediction Interval"),
                     lower = c(aux$ci.lb, aux$cr.lb),
                     upper = c(aux$ci.ub, aux$cr.ub),
                     group = "B"))
  res <- data.frame(res)
  res$byvar <- toupper(res$byvar)
  return(res)
}

@@

# Build forest plot for heterogeneous analysis
# Build plot function for forest plots
build_forest_het <- function(estims, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
  mod <- update(mod, byvar = hetvar, print.byvar = F)
